%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
%\usepackage{fontawesome}
%\usepackage{fontspec}
%\usepackage{tabularx}
%\usepackage{ragged2e}
\usepackage{tabto}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[margin=0.5in]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{7cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Karthik Ramaswamy}{Padmanabhan}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{San Francisco, CA 94131 }{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{909-839-3097}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
% \email{xpan1@swarthmore.edu}                               % optional, remove / comment the line if not wanted
% \homepage{shawnpan.me}                         % optional, remove / comment the line if not wanted
% \extrainfo{}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-15mm}

\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelope\enspace \href{mailto:karthikpad@gmail.com}{karthikrpad@gmail.com} & \faMobile\enspace 812-325-0180 & \faGlobe\enspace \href{https://www.karthikrp.com}{karthikrp.com} & \faLinkedin\enspace\href{https://www.linkedin.com/in/karthikrpad}{karthikrpad}\\  
\end{tabular}
\end{center}

\section{PROFESSIONAL SUMMARY}
{- Bioinformatics Expert with 10+ years of experience designing, developing, \& deploying NGS analysis pipelines. \\ 
- Proven track record of driving cross-functional collaboration, leading complex genomics projects, and delivering impactful tools for R\&D and clinical applications.}

%\section{TECHNICAL SKILLS}
%
%% {\customcvproject{Software/Tools}{}
%% {- Unix OS, R Bioconductor, RStudio, AWS, bioinformatics tools used in downstream analysis (QC, trimming, alignment, peak-calling, variant calling, sequence annotation, etc.), pathway/regulatory network analysis (iPathwayGuide), visualization (Cytoscape, R Shiny), Machine learning and feature selection (Random forests, Genetic Algorithms, Support Vector Machines), \LaTeX
%%   }
%% }
%{\customcvproject{Biological Data Analysis}{}
%{- bulk and scDNA-Seq (CNV and SNV calling, Bisulfite Sequencing, ChIP-Seq, (h)MeDIP-Seq, ATAC-Seq)\\
%- bulk and scRNA-Seq (Expression profiling, \textit{de novo} transcriptome assembly)}
%}
%%
%{\customcvproject{Bioinformatics Engineering}{}
%{- Python, R, Perl, Nextflow, Snakemake, AWS, R Shiny, Docker, Singularity, JavaScript, version control (CVS, git), Jupyter Notebook, SDLC best practices\\
%- Machine learning and feature selection (Random forests, Genetic Algorithms, Support Vector Machines)}
%}

% {\customcvproject{Databases}{}
% {- UCSC Genome Browser, NCBI, KEGG, Reactome, GEO, SRA, ENCODE, Gene Ontology, TCGA}
% }

\section{TECHNICAL SKILLS}
\begin{minipage}{\maincolumnwidth}%
	\small{
%	\textbf{Biological Data Analysis:}  CNV and SNV calling, Bisulfite Sequencing, ChIP-Seq, (h)MeDIP-Seq, ATAC-Seq, bulk and single cell RNA-Seq\\
%	\textbf{Languages:} Python, R, Perl, R Shiny\\
%	\textbf{Developer Tools:} Git, Docker,  Singularity, VS Code, AWS, Jupyter Notebook\\
%	\textbf{Pipelining Frameworks:} Nextflow, Snakemake}%
	
	\textbf{NGS Analysis:} CNV/SNV detection, ChIP-Seq, (h)MeDIP-Seq, ATAC-Seq, bulk/single-cell RNA-Seq, ONT, scCUT\&Tag\\
	\textbf{Programming \& Tools:} Python, R, Perl, Bash, R Shiny, Jupyter\\
	\textbf{Pipeline Development:} Nextflow, Snakemake, Docker, Singularity, Git\\
	\textbf{Cloud \& DevOps:} AWS (EC2, S3), CI/CD, GitHub, VS Code}%
\end{minipage}%

\section{BIOINFORMATICS EXPERIENCE}

{\customcventry{San Jose, CA}{Takara Bio USA}{Senior Staff Engineer, Bioinformatics}{Apr 2024 - present}{}
{- Architected and led the overhaul of the Cogent suite (DNA/RNA-Seq pipelines) using Nextflow, improving runtime efficiency and reducing pipeline failure rate\\
- Designed and deployed scalable tools for R\&D teams to accelerate new product design cycles, integrating Python, Docker, and Shiny for rapid prototyping
}


{\customcventry{San Jose, CA}{Takara Bio USA}{Staff Scientist, Bioinformatics}{Jan 2021 - Mar 2024}{}
{- Spearheaded pipeline development and UI implementation for Embgenix PGT-A, enabling reliable aneuploidy detection from low-pass CNV data\\
- Acted as the bioinformatics liaison for DNA-Seq reproductive health products, delivering insights for clinical assay development
}

{\customcventry{Ann Arbor, MI}{University of Michigan}{Bioinformatician/Computational Biologist}{Sep 2016 - Jan 2021}{}
{-Independently designed and operationalized robust Snakemake pipelines for high-dimensional genomics experiments (e.g., ChIP-Seq, WGBS, ATAC-Seq) used across multiple projects\\
- Initiated and led project scoping discussions, guiding PI-level decision-making on analysis plans, tool selection, and budget allocation
}
}

{\customcventry{West Lafayette, IN}{Purdue University}{Research Assistant}{Aug 2012 - Jul 2016}{}
{-Led the design and execution of a \textit{de novo} transcriptome analysis project in giant ragweed, uncovering candidate genes linked to herbicide resistance\\
- Developed and implemented statistical models for protein domain co-occurrence analysis across plant lineages, generating novel evolutionary insights into early land plant diversification
}

{\customcventry{Chesterfield, MO}{Monsanto}{Data Science Intern}{May 2015 - Aug 2015}{}
{-Built predictive ML models to correlate genetic and metabolite profiles with yield outcomes, identifying top-ranked features that informed product development\\
- Delivered findings through custom R Shiny dashboards used by cross-state R\&D teams}
}

\section{EDUCATION}
{\customcventry{West Lafayette, IN}{Purdue University}{Ph.D. Biological Sciences (Computational Life Sciences Program)}{Jul 2016}{}{}}
{\customcventry{Bloomington, IN}{Indiana University}{M.S. Bioinformatics}{Jun 2011}{}{}}
{\customcventry{Tamil Nadu, India}{SASTRA University}{B.Tech. Industrial Biotechnology}{May 2009}{}{}}

\section{PUBLICATIONS AND PATENTS}
\begin{minipage}{\maincolumnwidth}%
	\small{
	- J. Meyers, L. Zhao, N. Yasuyama, J. Kim, \textbf{K. Padmanabhan}, et al. "Evaluation of Cell-Free Nucleic Acids in Blastocoel Fluid Conditioned Media and its Potential for Non-Invasive Embryo Assessment". \textit{Fertility and Sterility}. 2022 Oct.\\
	- N.K. Patel, J.H. Nunez, M. Sorkin, S. Marini, C.A. Pagani, A.L. Strong, C.D. Hwang, S. Li, \textbf{K. Padmanabhan}, et al. "Macrophage TGF-$\beta$ signaling is critical for wound healing with heterotopic ossification after trauma".  \textit{JCI Insight}. 2022 Sep.\\
	- J. Foox, J. Nordlund, C. Lalancette, T. Gong, M. Lacey, S. Lent, B.W. Langhorst, V.K.C. Ponnaluri, L. Williams, \textbf{K. Padmanabhan}, et al. "The SEQC2 Epigenomics Quality Control (EpiQC) Study: Comprehensive Characterization of Epigenetic Methods, Reproducibility, and Quantification".  \textit{Genome Biology}. 2021 Dec.\\
	- J. Meyers, J. Laliberte, N. Yasuyama, J. Kim, \textbf{K. Padmanabhan}, et al. "The Effect of Embryo Morphology and Culturing Methods on the Performance of Non-Invasive Preimplantation Genetic Testing for Aneuploidies". \textit{Fertility and Sterility}. 2021 Sep.\\
	- Z.M. Laubach, J.R. Greenberg, J.W. Turner, T. Montgomery, M.O. Pioon, L. Smale, R. Cavalcante, \textbf{K. Padmanabhan}, et al. "Early-life social experience affects offspring DNA methylation and later life stress phenotype". \textit{Nature Communications}. 2021 Jul.\\
	- N.J. Edwards, E. Hobson, D. Dey, A. Rhodes, C. Pagani, A.L. Strong MD, G.E. Hespe, A. Huber, \textbf{K. Padmanabhan}, et al. "High Frequency Spectral Ultrasound Imaging Detects Early Stage Post Traumatic Heterotopic Ossification in Rodent Models". \textit{Stem Cells Dev}. 2021 May.\\
	- C.A. Pagani, A.K. Huber, C. Hwang, S. Marini, \textbf{K. Padmanabhan}, et al. "Novel Lineage Tracing System to Identify Site-specific Ectopic Bone Progenitor Cells". \textit{Stem Cell Reports}. 2021 Feb.\\
          - P. Venkatraman, I. Mills-Henry, \textbf{K. Padmanabhan}, et al. “Rods Contribute to Visual Behavior in Larval Zebrafish”. \textit{Investigative Ophthalmology and Visual Science}. 2020 Oct.\\
	- A.K. Huber, N. Patel, C.A. Pagani, S. Marini, \textbf{K. Padmanabhan}, et al. "Immobilization after injury alters extracellular matrix and stem cell fate". \textit{The Journal of Clinical Investigation}. 2020 Jul..\\
          - A.K Saha, R. Contreras-Galindo, Y.S. Niknafs, M. Iyer, T. Qin, \textbf{K. Padmanabhan}, et al. "The role of the histone H3 variant CENPA in prostate cancer". \textit{Journal of Biological Chemistry}. 2020 May.\\
	- \textbf{K. Padmanabhan}, K. Segobye, S.C. Weller, B. Schulz, M. Gribskov. "Preliminary investigation of glyphosate resistance mechanism in giant ragweed using transcriptome analysis". \textit{F1000 Research}. 2016 Jun.\\
	- B. Schulz, S.C. Weller, M. Gribskov, \textbf{K. Padmanabhan}, K. Segobye, "Diagnostic Tools for Herbicide Resistance in Weeds", Application No. 61/910,770 (“Technology”), 2013
	}%
\end{minipage}%


\section{PRESENTATIONS}
\begin{minipage}{\maincolumnwidth}%
	\small{
	- \textbf{K. Padmanabhan}, K. Segobye, S.C. Weller, B. Schulz, M. Gribskov, "Transcriptome Analysis of Giant Ragweed", Office of Interdisciplinary Graduate Programs Spring Reception, Purdue University, 2015 (Poster Presentation)\\
	- \textbf{K. Padmanabhan}, K. Segobye, M. Gribskov, B. Schulz, S.C. Weller, "Molecular Analysis of Glyphosate Resistance in Giant Ragweed", NCWSS Annual Meeting, Minneapolis, MN, December 3, 2014 (Oral Presentation)\\
	- \textbf{K. Padmanabhan}, K. Segobye, M. Gribskov, B. Schulz, S.C. Weller, "Molecular Analysis of Glyphosate Resistance in Giant Ragweed", Graduate Student Retreat, Purdue University, 2014 (Oral Presentation)\\
          - \textbf{K. Padmanabhan}, N.B. Best, M. Gribskov, S.C. Weller, B. Schulz, "Transcriptome Analysis of Glyphosate Resistance in Giant Ragweed", Joint Annual Meeting of WSSA and CWSS, Vancouver, BC, February 4, 2014 (Oral Presentation).  
	}%
\end{minipage}%

\section{SELECTED AWARDS}
\begin{minipage}{\maincolumnwidth}%
	\small{
	- Purdue Graduate Student Government Travel Award, Purdue University, 2015\\
          - Purdue Graduate Student Government Professional Award, Purdue University, 2014\\
          - Student Innovator Award, Purdue University, 2014\\
          - Summer Institutes in Statistical Genetics Travel Award, University of Washington, 2014\\
	- Best Oral Presentation, Department of Biological Sciences, Purdue University, 2014\\
	 - Dr. P.T. Gilham Graduate Award. Purdue University, 2011
	}%
\end{minipage}%
 
\section{OUTREACH AND LEADERSHIP}
\begin{minipage}{\maincolumnwidth}%
	\small{
	 - Volunteer Reviewer, PeerJ, 2024 - present\\
	 - Associate Editor, Journal of Emerging Investigators, 2024-25\\
          - Assistant Program Coordinator, LSAMP Summer Undergraduate Research Program, 2016\\
          - President/Treasurer/Webmaster, Biological Graduate Student Council, Purdue University, 2012-15\\
          - Organizer/Lead Instructor, Computational Interdisciplinary Graduate Programs RNA-Seq Workshop, 2015\\
          - Webmaster, Society of Industrial and Applied Mathematics, Purdue University, 2012-13\\
	- Teaching Assistant, Purdue University\\
\tabto{4mm} \bullet \textit{Introduction to R and Bioconductor, Summer 2014}\\ 
\tabto{4mm}\bullet  \textit{Human Anatomy and Physiology Fall 2011 – Spring 2013}
	}%
\end{minipage}%

}
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
